\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% -- Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% -- Sections Formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% -- Custom Commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemC}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}

\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -- Document/CV begins
\begin{document}

% -- [Header]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{https://www.linkedin.com/in/shaiqkar/}{\Large Shaiq Iqbal}} & Email : \href{mailto:shaiqkar@gmail.com}{shaiqkar@gmail.com}\\
	\href{https://www.linkedin.com/in/shaiqkar/}{{https://www.linkedin.com/in/shaiqkar/}} & Mobile : +917006343764 \\
\end{tabular*}

% -- [Education]
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Presidency University}{Bengaluru, India}
            {B.Tech in Computer Science;  CGPA: 8.3}{Aug 2018 -- Jun 2022}
    \resumeSubHeadingListEnd


% -- [Experience]
\section{Experience}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Webknot Technologies}{Bengaluru, Karnataka}
            {Senior Software Engineer}{Jul 2022 - Present}
        \resumeItemListStart
            \resumeItem
                {HDFC Mobile Banking}
                {Designed and implemented a data synchronization pipeline to efficiently update merchant billing details for the banking app. Leveraged GCS gRPC channels, Pub/Sub, and \textbf{PostgreSQL Copy} to reliably update more than \textbf{48K} merchant records with a \textbf{sub-3 second} processing time. Improved batch  performance by \textbf{12\%} by optimizing buffer allocation.}
            \resumeItemC
                {Developed a full-text search engine utilizing PostgreSQL full-text search capabilities, serving \textbf{10M} users. Optimized the solution by pre generating \textbf{8M} ts vectors based on merchant names, and leveraging Postgres functional indexes to enable sub-second query performance.}
            \resumeItemC
                {Written REST/gRPC API’s and Scalable Micro Services in Spring Boot, Golang and working with cross functional teams including Admin, CS, UPI and Net Banking.}
            \resumeItem
                {ScaleLinode (Collaboration with Akamai)}
                {Spearheaded the design and development of a highly available auto-scaling platform for virtual machines on Linode, replicating key AWS capabilities. Architected \textbf{15+} microservices on Kubernetes to manage VM lifecycle, secure credential storage, and CI/CD automation.}
            \resumeItemC
                {Created \textbf{Gather}, a real-time system metrics collection tool using gRPC streams, with concurrent data gathering of \textbf{20+} system metrics and \textbf{time-series} storage. Built internal Go packages including \textbf{Quark} for distributed ID generation and \textbf{kManager} for Helm and Kubernetes automation.}
            \resumeItem
                {Scorz (Large-scale multi-sensory in-home sports fan engagement)}{Streamlined IoT device onboarding by automating AWS certificate generation, firmware signing, and device provisioning processes, reducing deployment time from \textbf{7 days to 2 hours} and enabling secure production rollout of \textbf{4500} connected devices for WJHC and FIFA 2022.}      
            \resumeItemC
                {Refactored and migrated \textbf{11} Spring Boot microservices from version \textit{2.4.0 to 3.0.0}. Overall maintained \textbf{23} microservices and \textbf{Kafka Sync Connectors}.}
            \resumeItem
                {Pallete (Platform for communication and interaction among student stakeholders in US)}{Migrated PHP/MySQL configuration to \textbf{React, FastAPI with AWS Aurora}. Transitioned to AWS instance of \textbf{RHEL} with Amplify, resulting in a \textbf{37\%} cost reduction.}
            \resumeItem
                {Paws (CRM for Pallete)}
                {Led monolithic NestJS API refactoring to serverless AWS Lambda architecture achieving \textbf{30\%} faster response times and \textbf{65\%} cost reduction, while developing a multi-tenant JavaScript SDK library (similar to JSForce) that encapsulates CRM API access through asynchronous function calls for streamlined integration.}

        \resumeItemListEnd
    \resumeSubHeadingListEnd

% -- [Projects]
\section{Projects}
    \resumeSubHeadingListStart
        \resumeSubItem
            {Qode - Online code execution engine}
            {Developed a secure platform supporting \textbf{12} programming languages with concurrent user testing capabilities, implementing Redis-based queue management for load balancing, Linux cgroups isolation via Isolate for sandboxed execution, and Server-Sent Events for real-time output streaming.\\
	    \textbf{Technologies}: Go, Cgroups V2, Redis, Isolate, Docker | \textcolor{blue}{\href{https://github.com/shaiq-dev/qode}{GitHub}} - \textcolor{blue}{\href{https://qode.run}{Demo}}}
        \resumeSubItem
        {Panic Alarm}
        {A smartwatch powered by AWS IoT Core, to detect \textbf{Atrial fibrillation}, measure \textbf{sinus rhythm} (ECG), real time location tracking, heart health alerts and emergency triggers.\\
	\textbf{Technologies}: ESP8266, MAX30102, Aws IOT, Next.JS, Prisma Accelerate | \textcolor{blue}{\href{https://github.com/shaiq-dev/panic-alarm}{GitHub}} - \textcolor{blue}{\href{https://panicalarm.shaiq.dev}{Demo}}}
    \resumeSubHeadingListEnd
  
% -- [Skills]
\section{Skills}
    \resumeSubHeadingListStart
        \item{\textbf{Programming}: Proficient in Python, Java, C, Go. Experienced with JS/TS, PHP, SQL, Kotlin.}
        \item{\textbf{Frameworks}: Spring Boot, Mono, Mux, Next Js, Nest JS, FastAPI, Lambda, gRPC.}
        \item{\textbf{DevOps Tools and Utilities}: Git, Docker, AWS, GraphQL, MongoDB, PostgreSQL, Aerospike, Redis, Kafka, Aurora, Kubernetes.}
    \resumeSubHeadingListEnd

% -- Version
% -- It is replaced by the GitHub action with commit SHA when publishing to Cloudflare R2
\vspace{16pt}
\smallskip
\begin{footnotesize}
    GitHub \the\month.\the\year.__VERSION__
\end{footnotesize}


% -- Document Ends
\end{document}