
  
\cvsection{Projects}

\cvproject{PanicAlarm Watch}
\begin{itemize}
\item IoT-based smartwatch to help elderly people in case of danger; enabled with smart alerts and cardiac arrest/
Heart Attack detection.
\item \textbf{Technologies}: ESP8266, C++, Next.JS, Vercel, Graphql, MongoDB.\\
\textcolor{blue}{\href{https://github.com/shaiq-dev/PanicAlarm}{GitHub}} | \textcolor{blue}{\href{https://panicalarm.vercel.app}{Demo}}
\end{itemize}
\smallskip
\smallskip

\cvproject{IssNow}
\begin{itemize}
\item Real-time International Space Station monitoring  web app based on Server sent events. Supports email-based alerts for ISS passes above a location and some custom space station analytics.
\item \textbf{Technologies}: Python, FastAPI, Redis, Mapbox SDK, React JS (Typescript)\\
\textcolor{blue}{\href{https://github.com/shaiq-dev/server4issnow}{GitHub}} | \textcolor{blue}{\href{https://issnow.netlify.app}{Demo}}
\end{itemize}
\smallskip
\smallskip

\cvproject{Code Pair}
\begin{itemize}
\item An online code editor / compiler for pair programming, interviews, troubleshooting, teaching and more,  with video sharing and fully functional chat and managed storage.
\item \textbf{Technologies}: React, Nest, FastAPI, lambda, Go, AWS, Docker\\
\textcolor{blue}{\href{https://github.com/shaiq-dev/CodePair}{GitHub}} |
\textcolor{blue}{\href{https://codepair.vercel.app}{Demo}}
\end{itemize}
\smallskip
\smallskip

\cvproject{Triod}
\begin{itemize}
\item An open source programming language with no oop's, no garbage collector, only functions and some maths.
\item \textbf{Technologies}: : C Language\hspace{2mm}|\hspace{2mm}
\textcolor{blue}{\href{https://github.com/shaiq-dev/Triod}{GitHub}}
\end{itemize}
\smallskip

\cvsection{Achievements}
\begin{itemize}
\item Pre finalist \textbf{\textcolor{blue}{eYantra}} Robotic Competition 2020 conducted by \textbf{IIT Bombay}.
\item \textbf{\textcolor{blue}{Google} Cloud Career Readiness Program} recipient 2021.
\item \textbf{Google Cloud} badges in DevOps, Cloud Engineering, Kubernetes, and Networking from \textbf{\textcolor{blue}{\href{https://www.qwiklabs.com/public_profiles/c11f5195-2ad0-4404-83c4-08ad982d139c}{Qwiklabs}}}
\item Certifications in Python, Java, JS, React, REST API, and \textbf{Problem Solving} from 
\textbf{\textcolor{blue}{\href{https://www.hackerrank.com/shaiqkar}{Hackerrank}}}
\item \textbf{Postman student \textcolor{blue}{\href{https://shrtst.herokuapp.com/R3io}{expert}}}, API literacy.
\end{itemize}
\smallskip

\cvsection{Extracurricular}
\begin{itemize}
\item \textbf{\textcolor{blue}{Co-Founder and Student Convener}} of \textbf{Crescendo Developers Club}, Presidency University. The club aims at strengthening the roots of Computer Science and has more than 450 active student participants.
\end{itemize}